In-silico molecular enrichment and clearance of the human intracranial space

### 2024-11-28 paper/main.tex
Updates from Overleaf

\begin{figure}
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/Brain-PVS-callouts.png}
     \end{subfigure}
     \hfill
     \caption{a) Illustration of the different intracranial domains
       considered with labels;}
     \label{fig:intracranial_domains}
\end{figure}

@@

\begin{figure}[h!]
\centering 
\includegraphics[width = 0.9\linewidth]{figures/figure2.png}
\caption{
A) Illustration of 3D-domains; 
B) Illustration of relevant boundaries; 
C) schematic illustration of the model, its doamins and boundaries; 
D) CSF flow induced by CSF production; 
E) production-induced CSF velocities in the SAS and third and fourth ventricle (V3 \& V4); 
F) CSF flow induced by peak systolic expansion; 
G) cardiac dispersion enhancement factor;
H) CSF flow induced by respiration; 
I) respiratory dispersion enhancement factor;
J) cardiac-induced flow velocities;
K) cardiac-induced dispersion enhancement factor;
L) respiratory flow velocities;
M) respiratory dispersion enhancement factor;
N) sagittal, coronal and axial planes of tracer concentration after 1, 6, 12 and 24$\,$h for model A. The outer model boundaries is shown in cyan, the pial membrane in purple and the arteries in red.;
O) model X,Y and Z after 12h;
}
\label{fig:csf}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{paper/figures/figure1.png}
     \caption{a) Illustration of the different intracranial domains
       considered with labels;}
     \label{fig:intracranial_domains}
\end{figure}

@@

\begin{figure}[h!]
\centering 
\includegraphics[width = 0.9\linewidth]{figures/figure2.png}
\caption{
A) Illustration of 3D-domains; 
B) Illustration of relevant boundaries; 
C) schematic illustration of the model, its doamins and boundaries; 
D) CSF flow induced by CSF production; 
E) production-induced CSF velocities in the SAS and third and fourth ventricle (V3 \& V4); 
F) CSF flow induced by peak systolic expansion; 
G) cardiac dispersion enhancement factor;
H) CSF flow induced by respiration; 
I) respiratory dispersion enhancement factor;
J) cardiac-induced flow velocities;
K) cardiac-induced dispersion enhancement factor;
L) respiratory flow velocities;
M) respiratory dispersion enhancement factor;
N) sagittal, coronal and axial planes of tracer concentration after 12h in different model variations. The outer model boundaries is shown in cyan, the pial membrane in purple and the arteries in red.;
O) total content of tracer in each compartment;
P) mean tracer concentration in each compartment;
}
\label{fig:csf}
\end{figure}
